Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-19 paper/paper.tex
Add the map of unrecognized states #58

\subsection{Boundaries for unrecognized states}
To recover economic growth rates in unrecognized states, we also need to aggregate nighttime light data into the level of these breakaway territories. The spatial data sources for the boundaries of unrecognized states differ by each:
\paragraph{Nagorno-Karabakh and Azerbaijan proper}
The data on the internationally recognized boundary of Azerbaijan (which includes the western and southern boundaries of Nagorno-Karabakh) is obtained from ACASIAN (2014). This dataset was created in conjunction with the Institute of Geography at Russian Academy of Sciences, with the official map definitive as of the 1989 Soviet Census.

@@

>>>>

\subsection{Boundaries for unrecognized states}
To recover economic growth rates in unrecognized states, we also need to aggregate nighttime light data into the level of these breakaway territories. The spatial data sources for the boundaries of unrecognized states differ by each. Figure \ref{map} shows these boundary data.
\paragraph{Nagorno-Karabakh and Azerbaijan proper}
The data on the internationally recognized boundary of Azerbaijan (which includes the western and southern boundaries of Nagorno-Karabakh) is obtained from ACASIAN (2014). This dataset was created in conjunction with the Institute of Geography at Russian Academy of Sciences, with the official map definitive as of the 1989 Soviet Census.

@@

\clearpage

\begin{figure}[ptb]
\caption{Unrecognized States in the Former Soviet Union}
\includegraphics[width=\linewidth]{map.png}
\label{map}%
{\scriptsize \textbf{Notes}: 
	The data sources are GADM (2018) for international boundaries and for Transnistria; ACASIAN (2014) for Abkhazia and South Ossetia; and Armenian Ministry of Foreign Affairs (2018) for Nagorno-Karabakh. WGS 1984 is used as the coordinate system to draw the map.
}
\end{figure}
